\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-19 paper_resources/doc/paper.tex
Update...

%https://www.thekerneltrip.com/machine/learning/computational-complexity-learning-algorithms/
%https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization, LU decomposition, Winograd or Strassen algorithm, just to name a few, may be used depending on solver of linear equations as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}. For example, by Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications, needs $d^3$ computation cost to find an inverse of the matrix associated to the linear system, where $d$ stands for the number of input features. It is worth to mention that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent. Using Gradient Descent (GD),  the above complexity reduces to $O(n^2d )$. The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges. Therefore, when comes to input data with large number of features, GS is preferred over OLS.

>>>>

%https://www.thekerneltrip.com/machine/learning/computational-complexity-learning-algorithms/
%https://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation %https://levelup.gitconnected.com/train-test-complexity-and-space-complexity-of-linear-regression-26b604dcdfa3
To solve a linear system of $(d+1)$ unknowns and $d+1$ linear equations involved,  Cholesky  factorization or LU decomposition for matrix inversion, and Winograd or Strassen algorithm for matrix multiplication depending on a solver of linear equations chosen as well as the sparsity of the matrix associated to the linear system~\cite{krishnamoorthy2013matrix}. For example, by using Cholesky decomposition, solving the system requires a matrix inversions and matrix multiplications;  computation cost of $d^3$ is required to find an inverse of the matrix associated to the linear system, which is the most consuming part of the algorithm. Thus, OLS using close-form matrix techniques performs in $O(d^3)$ time complexity.  %, where $d$ stands for the number of input features. 
It is worth mentioning that when the number of input features becomes large, these closed-form matrix techniques are usually replaced by iterative ones, such as gradient descent (GD)~\cite{andrychowicz2016learning}. Using GD,  the above complexity reduces to $O(n^2d )$. The learning rate in GD has to be carefully chosen, as it dictates how quick the algorithm is and how fast it converges. Therefore, when comes to input data with large number of features, GS is preferred over OLS.
